---
title: "Ch3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
library(tidyverse)
```

Question: do cars with big engines use more fuel than cars with small engines?
Hypothesis: Yes they do. small cars are more fuel efficient.

```{r}
ggplot2::mpg

```

displ=engine size in L
hwy=mpg

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

## 3.2.4 Exercises

```{r}
ggplot2::mpg
```
What do you see? 
a table of the data that is in ggplot2
How many rows in mpg? how many columns?
234 rows and 11 columns
what does the drv variable describe? (help>mpg)
what type of drive the car is.(four wheel, back wheel, front wheel)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```
why is this not helpful?
does not give any proportions or tell us anything about mpg


## 3.3.1 Exercises

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
What is wrong with this code and why is it not blue?
the color was put into the aes ()  when I took it out, it worked
Which variables are categorical? continuous?
Categorical = model, year, cyl, trans, drv, fl, class
continuous = displ, city, hwy
