---
title: "Ch3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
library(tidyverse)
```

Question: do cars with big engines use more fuel than cars with small engines?
Hypothesis: Yes they do. small cars are more fuel efficient.

```{r}
ggplot2::mpg

```

displ=engine size in L
hwy=mpg

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

## 3.2.4 Exercises

```{r}
ggplot2::mpg
```
What do you see? 
a table of the data that is in ggplot2
How many rows in mpg? how many columns?
234 rows and 11 columns
what does the drv variable describe? (help>mpg)
what type of drive the car is.(four wheel, back wheel, front wheel)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl))
```
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```
why is this not helpful?
does not give any proportions or tell us anything about mpg


## 3.3.1 Exercises

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
What is wrong with this code and why is it not blue?
the color was put into the aes ()  when I took it out, it worked
Which variables are categorical? continuous?
Categorical = model, year, cyl, trans, drv, fl, class
continuous = displ, city, hwy
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

```{r}
ggpolt(data = mpg) +
  geom_point(mapping = aes())
```

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```
               
## 3.5.1 Exercises
```{r, eval=FALSE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ city, nrow = 2)
```
when you facet wrap a continuous variable you get an error message.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ cyl)
```
the empty cells mean that there are no vehicles with that drv and cyl (ie no 5 cylinder 4 wheel drive cars)
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl))
```
essentially shows the same thing just without the additional data that the first one had
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```
the dot is like a place holder and makes it so you only have one facet
it also determines which side the facet will be on
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~ class, nrow = 2)
```
the advatages to facet instead of colors would be that there is no overlapping the disadvantage could be that it is a bit harder to compare side by side because they are all seperated
nrow is the number of rows 
ncol is the number of columns
grid does not use rows or columns

## 3.6.1 Exercises
geom_line, geom_boxplot, geom_histogram, geom_area
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) +
geom_point() +
geom_smooth(se = FALSE)
```
show.legend = false hides the legend
se = false will hide the confidence level around the smooth part of the figure
no the graphs will not look different because they are the same info just in a different order

## 3.7.1 Exercises
according to help, the default geom is histogram and freqpoly
geom_bar is for one variable and geom_col is for two variables
geom_smooth uses two continuous variables it can be controlled with x,y,alpha,color, fill, group, linetype, size, and weight
the y needs to be specified?